Quantile Regressions via Method of Moments with multiple fixed effects \tnoteref{t1}

### 2023-11-08 article/article.qmd
s
s

---
title: Quantile Regressions via Method of Moments with multiple fixed effects
author:
  - name: Fernando Rios-Avila
    email: friosavi@levy.org
    affiliations: 
        - id: levy
          name: Levy Economics Institute of Bard College          
    attributes:
        corresponding: true
  - name: Leonardo Siles
    email: leonardosiles@hotmail.com
    affiliations:
        - name: Universidad Católica Boliviana
          id: ucb
  - name: Gustavo Canavire-Bacarreza
    email: gcanavire@worldbank.org
    affiliations:
        - id: wb
          name: World Bank
    note: |
      The opinions expressed in this paper are those of the authors and do not necessarily reflect the views of the World Bank, its Board of Directors, or the countries it represents         
abstract: |
  This paper proposes a new method to estimate quantile regressions with multiple fixed effects. The method expands on the strategy proposed by @mss2019, allowing for multiple fixed effects, and providing various alternatives for the estimation of Standard errors. We provide Monte Carlo simulations to show the finite sample properties of the proposed method in the presence of two sets of fixed effects. Finally, we apply the proposed method to estimate the determinants of the surplus of government as a share of GDP allowing for both time and country fixed effects.
keywords: 
  - Fixed effects
  - Linear heteroskedasticity
  - Location-scale model
  - Quantile regression

date: last-modified
bibliography: bibliography.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal Name
      formatting: review
      model: 1p
      cite-style: authoryear
      number-depth: 2
---

>>>>

---
title: Quantile Regressions via Method of Moments with multiple fixed effects \tnoteref{t1}
author:
  - name: Fernando Rios-Avila
    email: friosavi@levy.org
    affiliations: 
        - id: levy
          name: Levy Economics Institute of Bard College          
    attributes:
        corresponding: true
  - name: Leonardo Siles
    email: leonardosiles@hotmail.com
    affiliations:
        - name: Universidad Católica Boliviana
          id: ucb
  - name: Gustavo Canavire-Bacarreza
    email: gcanavire@worldbank.org
    affiliations:
        - id: wb
          name: World Bank                 
abstract: |
  This paper proposes a new method to estimate quantile regressions with multiple fixed effects. The method expands on the strategy proposed by @mss2019, allowing for multiple fixed effects, and providing various alternatives for the estimation of Standard errors. We provide Monte Carlo simulations to show the finite sample properties of the proposed method in the presence of two sets of fixed effects. Finally, we apply the proposed method to estimate the determinants of the surplus of government as a share of GDP allowing for both time and country fixed effects.
keywords: 
  - Fixed effects
  - Linear heteroskedasticity
  - Location-scale model
  - Quantile regression

date: last-modified
bibliography: bibliography.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal Name
      formatting: review
      model: 1p
      cite-style: authoryear
      number-depth: 2
include-in-header: 
      text: |
        \tnotetext[t1]{The opinions expressed in this paper are those of the authors and do not necessarily reflect the views of the World Bank, its Board of Directors, or the countries it represents.}        
---
